CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-26 paper/ms.tex
Add trivial case where all B, N equal

\subsection{Noise-limited Regime} \label{ssec:noise_limited}
We consider the noise-limited regime. In this case, we assume that $N_i \gg
P_i$, so that Equation~\ref{eq:var_cov} reduces to
\beq \label{eq:var_cov_noise}
\begin{split}
\Var{\xps{i}{j}} &= N_iN_j \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= 0 \text{.}
\end{split}
\eeq
We will also assume a white noise spectrum, so that each $N_i$ is a constant
value. In this case, the computation of the Fisher matrix is quite simple. In
fact, we can rewrite it as
\beq\label{eq:fisher_noisedom}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Var{\hat{P}_{l,l'}(k)}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_j}\text{.}
\eeq
For a diagonal element, we can see that we will only get terms when $l=i$ or $l'=i$. Therefore
\beq\label{eq:fisher_noisedom2}
F_{i,i} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\denps(k)^2\text{.}
\eeq
Since we are assuming a white noise power spectrum, if we define
\begin{equation*}
V_k = \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
\end{equation*}
then we can simplify Equation~\ref{eq:fisher_noisedom2} to
\beq\label{eq:fisher_noisedom_diag}
F_{i,i} = 
V_k
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\text{.}
\eeq
For the off-diagonal case, we can see that the only term that will contribute
is when $l=i$ and $l'=j$, or vice-versa. Therefore, we have that
\beq\label{eq:fisher_noisedom_offdiag}
F_{i,j} = V_k
\frac{B_iB_j}{N_iN_j}\text{.}
\eeq
Note that as the number of fields increases, the diagonal elements become much
larger than the off-diagonal elements, assuming the magnitudes of all the
$B_i$'s and $N_i$'s are roughly similar. Therefore, the Fisher matrix becomes
approximately diagonal, as does the covariance matrix, and the errors on the
$B_i$'s become uncorrelated. This matches our naive expectation that
considering additional fields should reduce the degeneracies between each
$B_i$.

>>>>

\subsection{Noise-limited Regime} \label{ssec:noise_limited}
We consider the noise-limited regime. In this case, we assume that $N_i \gg
P_i$, so that Equation~\ref{eq:var_cov} reduces to
\beq \label{eq:var_cov_noise}
\begin{split}
\Var{\xps{i}{j}} &= N_iN_j \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= 0 \text{.}
\end{split}
\eeq
We will also assume a white noise spectrum, so that each $N_i$ is a constant
value. In this case, the computation of the Fisher matrix is quite simple. In
fact, we can rewrite it as
\beq\label{eq:fisher_noisedom}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Var{\hat{P}_{l,l'}(k)}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_j}\text{.}
\eeq
For a diagonal element, we can see that we will only get terms when $l=i$ or $l'=i$. Therefore
\beq\label{eq:fisher_noisedom2}
F_{i,i} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\denps(k)^2\text{.}
\eeq
Since we are assuming a white noise power spectrum, if we define
\begin{equation*}
V_k \equiv \int \frac{\text{d}k\,k^2}{2\pi^2} \denps(k)^2 V_{\text{surv}}\text{,}
\end{equation*}
then we can simplify Equation~\ref{eq:fisher_noisedom2} to
\beq\label{eq:fisher_noisedom_diag}
F_{i,i} = 
V_k
\sum_{\substack{l\neq i}}
\frac{B_l^2}{N_iN_l}\text{.}
\eeq
For the off-diagonal case, we can see that the only term that will contribute
is when $l=i$ and $l'=j$, or vice-versa. Therefore, we have that
\beq\label{eq:fisher_noisedom_offdiag}
F_{i,j} = V_k
\frac{B_iB_j}{N_iN_j}\text{.}
\eeq
Note that as the number of fields increases, the diagonal elements become much
larger than the off-diagonal elements, assuming the magnitudes of all the
$B_i$'s and $N_i$'s are roughly similar. Therefore, the Fisher matrix becomes
approximately diagonal, as does the covariance matrix, and the errors on the
$B_i$'s become uncorrelated. This matches our naive expectation that
considering additional fields should reduce the degeneracies between each
$B_i$.

Consider the extremely trivial case such that $B_i = B$ and $N_i = N$ for all
lines $i$. In this case, if we have $n_l$ lines, the Fisher matrix reduces to
\beq\label{eq:fisher_supertrivial}
        F_{i,j} = V_k \frac{B^2}{N^2} \times
        \begin{cases}
             n_l-1 & \text{if $i=j$} \\
             1 &\text{if $i\neq j$} \\
        \end{cases}\text{.}
\eeq
In the large $n_l$ limit, the Fisher matrix becomes diagonal, and we can
therefore write the covariance matrix as
\beq\label{eq:cov_supertrivial_largen}
C_{i,j} = \frac{N^2}{V_k B^2} \frac{1}{n_l-1} \delta_{ij}\text{,}
\eeq
where $\delta_{ij}$ is the Kronecker delta. This leads us to the conclusion
that in the noise-dominated regime where each line has comparable
$\text{S}/\text{N}$, the constraining power on each line $i$ scales as
$1/n_l$. In other words, one can improve the constraint on $B_i$ without
executing additional observations of line $i$.
